\chapter{Configurations}\label{configurations}

\section{Introduction}\label{introduction-1}

The size and implementation style of the memory is defined via HDL parameters. These are specified in the following section.

\section{Core Parameters}\label{core-parameters}

\begin{longtable}[]{@{}llcl@{}}
	\toprule
	Parameter                   & Type    & Default & Description\tabularnewline
	\midrule
	\endhead
	\texttt{MEM\_DEPTH}         & Integer & 256     & Memory Depth (Words)\tabularnewline
	\texttt{HADDR\_SIZE}        & Integer & 32      & Address Bus Size (Bits)\tabularnewline
	\texttt{HDATA\_SIZE}        & Integer & 32      & Data Bus Size (Bits)\tabularnewline
	\texttt{TECHNOLOGY}         & String  & GENERIC & Implementation Technology\tabularnewline
	\texttt{REGISTERED\_OUTPUT} & String  & NO      & Is output registered?\tabularnewline
	\bottomrule
	\caption{AHB-Lite Memory Parameters}
\end{longtable}


 \subsection{MEM\_DEPTH}\label{mem_depth}

\texttt{MEM\_DEPTH} defines the depth of the memory -- i.e. number of \texttt{HDATA\_SIZE}
words to be stored. The maximum depth supported is dependent upon the
target technology chosen.

 \subsection{HADDR\_SIZE}\label{haddr_size}

The \texttt{HADDR\_SIZE} parameter specifies the address bus size to connect 
to the AHB-Lite based host. The maximum size supported is 32 bits.

 \subsection{HDATA\_SIZE}\label{hdata_size}

The \texttt{HDATA\_SIZE} parameter specifies the data bus size to connect to 
the AHB-Lite based host. The maximum size supported is 32 bits.

 \subsection{TECHNOLOGY}\label{technology}

The \texttt{TECHNOLOGY} parameter defines the target silicon technology and 
may be one of the following values:

\begin{longtable}[]{@{}ll@{}}
	\toprule
	Parameter Value & Description\tabularnewline
	\midrule
	\endhead
	GENERIC & Behavioural (FPGA) Implementation\tabularnewline
	N3X & eASIC Nextreme-3 Structured ASIC\tabularnewline
	N3XS & eASIC Nextreme-3S Structured ASIC\tabularnewline
	\bottomrule
	\caption{Supported Technology Targets}
\end{longtable}

Details of the implementations corresponding to these parameter values can be found in Section 6, Technology Support

 \subsection{REGISTERED\_OUTPUT}\label{registered_output}

The \texttt{REGISTERED\_OUTPUT} parameter defines if the output of the memory 
is registered on assertion of the HREADY signal. It is specified as 
`YES' or `NO' (default).
