\chapter{Technology Support} \label{technology-support}

Physical memory implementation in silicon depends on the target
technology chosen. The AHB-Lite Memory IP allows a designer to
specify either a generic (i.e. behavioural) implementation or one 
of multiple technology-specific implementations via the \texttt{TECHNOLOGY} 
parameter. This section provides details of these implementations

 \section{GENERIC Implementation} \label{generic-implementation}

The \texttt{GENERIC} option is used to implement regular behavioural HDL allowing
both the physical implementation to be controlled during hardware
synthesis and full behavioural simulation to be performed.
Use this option to infer memories for technologies that support this, like FPGAs.

 \section{eASIC Structured ASIC Support} \label{easic-structured-asic-support}

The IP supports the Nextreme-3 and Nextreme-3S families as described
below. Please refer to the relevant technology datasheets for complete
details of the memory structures referenced.

 \subsection{Nextreme-3 Implementation (N3X)} \label{nextreme-3-implementation-n3x}

The Nextreme-3 family of devices features 9Kbit memory blocks, referred
to as `bRAM'. When the \texttt{TECHNOLOGY} parameter is defined as `N3X', all
memory will be implemented using 9Kbit bRAM cells.

 \subsection{Nextreme-3S Implementation (N3XS)} \label{nextreme-3s-implementation-n3xs}

The Nextreme-3S series of devices features separate 2Kbit and 18Kbit
memory blocks, referred to as `bRAM2K' and `bRAM18K' respectively. The
choice of which of these blocks are implemented when the \texttt{TECHNOLOGY}
parameter is defined as `N3XS' is as follows:

\begin{longtable}[]{@{}cll@{}}
	\toprule
	TECHNOLOGY & Memory Size & Implementation\tabularnewline
	\midrule
	\endhead
	N3XS & $\leqslant$4096 bits & bRAM2K blocks only\tabularnewline
	N3XS & \textgreater{}4096 bits & bRAM18K blocks only\tabularnewline
	\bottomrule
	\caption{Nextreme-3S Memory Implementation Styles}
\end{longtable}
